A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Electron Beam Dynamics

### 2018-09-29 paper/theor-experiment.tex
fixing units

\def \gunheight {25}
\def \quadheight {35}
\def \quadleft {127}
\def \kickerleft {160}
\def \leftarrow{10}
\def \bottomofarrows {29}
\def \topofarrows {34}
\begin{figure*}
	\begin{tikzpicture}[every node/.style={anchor=south west,inner sep=0pt},x=1mm, y=1mm,]   
	\node (fig1) at (0,0)
	{\includegraphics[width=\textwidth]{Report/awa-drawing}};
	\node[fill=white, inner sep=2pt] (txt2) at (0,\gunheight) {\large Gun};
	\node[fill=white, inner sep=2pt] (txt2) at (20,\gunheight) {\large Accelerating Cavities};
	\node[fill=white, inner sep=2pt] (txt2) at (\quadleft,\quadheight) {\large Quadrupoles};
	\draw [blue, ->, line width=1] (\quadleft+\leftarrow,\topofarrows) -- (\quadleft+\leftarrow, \bottomofarrows);
	\node[fill=white, inner sep=2pt] (txt2) at (\kickerleft,20) {\large $s_1$};
	\node[fill=white, inner sep=2pt] (txt2) at (\kickerleft+8,20) {\large $s_2$};
	\node[fill=white, inner sep=2pt] (txt2) at (\kickerleft,\quadheight) {\large Kicker};
	\draw [blue, ->, line width=1] (\kickerleft+\leftarrow-3,\topofarrows) -- (\kickerleft+\leftarrow-3, \bottomofarrows);	
	\draw [black, ->, line width=1] (0,-2) -- (100, -2);
	\node[fill=white, inner sep=2pt] (txt2) at (50,0) {\large Beam Direction};
	\end{tikzpicture}
	\caption{Side view of the high charge linac at the AWA. 
		All hardware in this drawing is currently installed.}
	\label{awa-linac}
	\vspace{-7em}
\end{figure*}

\def \septheight {65}
\def \bottomarrow {57}
\def \kleft {13}
\def \sleft {41.5}
\def \sheight {47}
\def \beam {35}
\begin{figure*}
	\begin{tikzpicture}[every node/.style={anchor=south west,inner sep=0pt},x=1mm, y=1mm,]   
	\node (fig2) at (0,0)
	{\includegraphics[width=\textwidth]{Report/tba_dogleg}};
	\node[fill=white, inner sep=2pt] (txt2) at (3,\sheight) {\large $s_1$};
	\node[fill=white, inner sep=2pt] (txt2) at (20,\sheight) {\large $s_2$};
	\node[fill=white, inner sep=2pt] (txt2) at (46,45) {\large $s_3$};
	\node[fill=white, inner sep=2pt] (txt2) at (33,\septheight) {\large Septum};
	\draw [blue, ->, line width=1] (\sleft,\septheight) -- (\sleft, \bottomarrow);	
	\node[fill=white, inner sep=2pt] (txt2) at (7,\septheight) {\large Kicker};
	\draw [blue, ->, line width=1] (\kleft,\septheight) -- (\kleft, \bottomarrow);
	\draw [black, ->, line width=1] (0,\beam) -- (100,\beam);
	\node[fill=white, inner sep=2pt] (txt2) at (50,\beam+2) {\large Beam Direction};
	\end{tikzpicture}
	\vspace{-12em}
	\caption{Continuation of the high charge beam line layout at the AWA, top view. 
		This is the proposed two beam acceleration section. 
		Only the kicker in this drawing is installed}
	\label{awa-tba}
\end{figure*}
%
%\vspace{-1em}

@@

The maximum number of individuals per generation was fixed at 80, 
Each experiment was allowed to run for twenty four hours, with 
a maximum generation limit of 100. 
We reduced the six objectives to four, 
and shortened the simulation time by moving the objectives further 
upstream to $s_1$ and $s_2$, the locations before and after the kicker.

@@

After collection of the data for all four experiments, several metrics
were compared, including number of generations completed in twenty four hours and
Pareto fronts at $s_1$ and $s_2$.
From Table \ref{extable}, we clearly see ex-3 is significantly 
slower, as it evaluated only 53 generations 
compared to the experiment with the maximum number, ex-1 at 96 generations.
Perhaps this trade off would be acceptable if the Pareto front was significantly 
improved, but from Fig. \ref{expareto}, we can see this is not the case.
Similar arguments can be made for ex-2, which evaluated about 15 less generations
with no clear benefit in either Pareto front.
The Pareto fronts at $s_1$, are nearly identical. We could expect
this trend would continue given more time. 
When looking at the Pareto front at $s_2$, only ex-4 has a slight 
edge over the others.
With ex-2 and ex-3 eliminated due to evaluation time, 
and a slightly better Pareto front at $s_2$ for ex-4, the hyper parameters in ex-4 were chosen as the default values for subsequent runs.

@@

\subsubsection{TBA Optimization Problem}
With computational and hyper parameters set, 
the full optimization problem of interest is explored.
The objectives (beam sizes and energy spread) are calculated at 
$s_3=19.4$~m, located downstream of the septum, see Fig.~\ref{awa-tba}. 
Given the longitudinal location of $s_3$ (unless otherwise noted), 
we define the objectives and input parameters as:
\begin{align}
\text{min}  \quad & \text{rms}_{x}, \quad \text{rms}_{y} \label{eq:awa:p1}\\
& \text{rms}_{px}, \quad \text{rms}_{py}, \label{eq:awa:p2}\\
& \text{rms}_{s}, \quad dE \label{eq:awa:p4} \\
\text{constraints} \quad & rms_x < 0.1 \, [m] |_{s=s_1}\label{eq:awa:c1}\\
\quad & rms_y < 0.1 [m] |_{s=s_1}\, \label{eq:awa:c2}\\
\quad & |rms_y - rms_x | < 0.005 \, [m] |_{s=s_1}\label{eq:awa:c3}\\
\text{subject to} \quad & q = 40 \left[\text{nC}\right] \label{eq:awa:firstconstr}\\
\quad & \text{Volt}_{\text{Gun}} = 64\left[\text{MV/m}\right] \label{eq:awa:lastconstr}\\
\quad & \text{Volt}_{\text{Linac}} = 24 \, \text{or} \, 25\left[\text{MV/m}\right] \\
\quad & R_x = R_y = 9 \left[\text{mm}\right] \label{eq:awa:firstdvar}\\
\quad & \phi_{\text{gun}} =-20^\circ \label{eq:awa:gphidvar}\\
\quad & \phi_{\text{linac}} =-20^\circ \label{eq:awa:lastdvar}
\end{align}

>>>>

\def \gunheight {25}
\def \quadheight {35}
\def \quadleft {127}
\def \kickerleft {160}
\def \leftarrow{10}
\def \bottomofarrows {29}
\def \topofarrows {34}
\begin{figure*}
	\begin{tikzpicture}[every node/.style={anchor=south west,inner sep=0pt},x=1mm, y=1mm,]   
	\node (fig1) at (0,0)
	{\includegraphics[width=\textwidth]{Report/awa-drawing}};
	\node[fill=white, inner sep=2pt] (txt2) at (0,\gunheight) {\large Gun};
	\node[fill=white, inner sep=2pt] (txt2) at (20,\gunheight) {\large Accelerating Cavities};
	\node[fill=white, inner sep=2pt] (txt2) at (\quadleft,\quadheight) {\large Quadrupoles};
	\draw [blue, ->, line width=1] (\quadleft+\leftarrow,\topofarrows) -- (\quadleft+\leftarrow, \bottomofarrows);
	\node[fill=white, inner sep=2pt] (txt2) at (\kickerleft,20) {\large $s_1$};
	\node[fill=white, inner sep=2pt] (txt2) at (\kickerleft+8,20) {\large $s_2$};
	\node[fill=white, inner sep=2pt] (txt2) at (\kickerleft,\quadheight) {\large Kicker};
	\draw [blue, ->, line width=1] (\kickerleft+\leftarrow-3,\topofarrows) -- (\kickerleft+\leftarrow-3, \bottomofarrows);	
	\draw [black, ->, line width=1] (0,-2) -- (100, -2);
	\node[fill=white, inner sep=2pt] (txt2) at (50,0) {\large Beam Direction};
	\end{tikzpicture}
	\caption{Side view of the high charge linac at the AWA. 
		All hardware in this drawing is currently installed. 
	Note locations $s_1$ and $s_2$, before and after the kicker.}
	\label{awa-linac}
	\vspace{-7em}
\end{figure*}

\def \septheight {65}
\def \bottomarrow {57}
\def \kleft {13}
\def \sleft {41.5}
\def \sheight {47}
\def \beam {35}
\begin{figure*}
	\begin{tikzpicture}[every node/.style={anchor=south west,inner sep=0pt},x=1mm, y=1mm,]   
	\node (fig2) at (0,0)
	{\includegraphics[width=\textwidth]{Report/tba_dogleg}};
	\node[fill=white, inner sep=2pt] (txt2) at (3,\sheight) {\large $s_1$};
	\node[fill=white, inner sep=2pt] (txt2) at (20,\sheight) {\large $s_2$};
	\node[fill=white, inner sep=2pt] (txt2) at (46,45) {\large $s_3$};
	\node[fill=white, inner sep=2pt] (txt2) at (33,\septheight) {\large Septum};
	\draw [blue, ->, line width=1] (\sleft,\septheight) -- (\sleft, \bottomarrow);	
	\node[fill=white, inner sep=2pt] (txt2) at (7,\septheight) {\large Kicker};
	\draw [blue, ->, line width=1] (\kleft,\septheight) -- (\kleft, \bottomarrow);
	\draw [black, ->, line width=1] (0,\beam) -- (100,\beam);
	\node[fill=white, inner sep=2pt] (txt2) at (50,\beam+2) {\large Beam Direction};
	\end{tikzpicture}
	\vspace{-12em}
	\caption{Continuation of the high charge beam line layout at the AWA, top view. 
		This is the proposed two beam acceleration section. 
		Only the kicker in this drawing is installed. 
	Note $s_3$, the entrance to the fifth quadrupole on the beam line.
	This is the optimization location.}
	\label{awa-tba}
\end{figure*}
%
%\vspace{-1em}

@@

The maximum number of individuals per generation was fixed at 80. 
This number was chosen based on the node architecture, and the 
to prevent a prohibitive computational cost.  
Each experiment was allowed to run for twenty four hours, with 
a maximum generation limit of 100. 
We reduced the six objectives to four, 
and shortened the simulation time by moving the objectives further 
upstream to $s_1$ and $s_2$, the locations before and after the kicker, 
see Fig.~\ref{awa-tba}.

@@

After collection of the data for all four experiments, several metrics
were compared, including number of generations completed in twenty four hours and
Pareto fronts at $s_1$ and $s_2$, see Fig.~\ref{awa-linac}.
From Table \ref{extable}, we clearly see ex-3 is significantly 
slower, as it evaluated only 53 generations 
compared to the experiment with the maximum number, ex-1 at 96 generations.
Perhaps this trade off would be acceptable if the Pareto front was significantly 
improved, but from Fig. \ref{expareto}, we can see this is not the case.
Similar arguments can be made for ex-2, which evaluated about 15 less generations.
The Pareto fronts at $s_2$, are nearly identical. We could expect
this trend would continue given more time. 
When looking at the Pareto front at $s_1$, only ex-4 has a slightly 
larger range compared to the others.
With ex-2 and ex-3 eliminated due to evaluation time, 
and a slightly better Pareto front at $s_1$ for ex-4, 
the hyper parameters in ex-4 were chosen as the default values for subsequent runs.

@@

\subsubsection{TBA Optimization Problem}
With computational and hyper parameters set, 
the full optimization problem of interest is explored.
The objectives (beam sizes and energy spread) are calculated at 
$s_3=19.4$~m, located downstream of the septum, see Fig.~\ref{awa-tba}. 
Given the longitudinal location of $s_3$ (unless otherwise noted), 
we define the objectives and input parameters as:
\begin{align}
\text{min}  \quad & \text{rms}_{x}, \quad \text{rms}_{y} \label{eq:awa:p1}\\
& \text{rms}_{px}, \quad \text{rms}_{py}, \label{eq:awa:p2}\\
& \text{rms}_{s}, \quad dE \label{eq:awa:p4} \\
\text{constraints} \quad & rms_x < 0.1 \, (m) |_{s=s_1}\label{eq:awa:c1}\\
\quad & rms_y < 0.1\, (m) |_{s=s_1}\, \label{eq:awa:c2}\\
\quad & |rms_y - rms_x | < 0.005 \, (m) |_{s=s_1}\label{eq:awa:c3}\\
\text{subject to} \quad & q = 40 \, (nC) \label{eq:awa:firstconstr}\\
\quad & \text{Volt}_{\text{Gun}} = 64 \, \, (\text{MV/m}) \label{eq:awa:lastconstr}\\
\quad & \text{Volt}_{\text{Linac}} = 24 \, \text{or} \, 25\,\, (\text{MV/m}) \\
\quad & R_x = R_y = 9 \, (mm) \label{eq:awa:firstdvar}\\
\quad & \phi_{\text{gun}} =-20^\circ \label{eq:awa:gphidvar}\\
\quad & \phi_{\text{linac}} =-20^\circ \label{eq:awa:lastdvar}
\end{align}
